%%% Author: mterenui (F.M.T.C)
%%% Docs: https://github.com/xxx
%%% License: GNU General Public License v3.0
%%% This document is provided as a general template for informational purposes only and does not constitute legal advice. Permission is granted to copy, modify, and use this template for personal or commercial purposes, provided that this copyright and license notice is retained in all copies or substantial portions of the document. The author makes no representations or warranties regarding the legal validity or enforceability of this template in any jurisdiction. Users are strongly encouraged to consult a qualified legal professional before using this document.

\section{Ownership of Materials}
\label{sec:ownership}

All photographs, video recordings, audio recordings, digital files, negatives, transparencies, raw files, edited files, and any other media captured during the session (collectively, the “Materials”) shall remain the sole and exclusive property of the Photographer and/or Company.

\subsection{Copyright Ownership}
All copyrights and intellectual property rights in the Materials are and shall remain vested exclusively in the Photographer and/or Company, pursuant to applicable copyright laws. Nothing in this Agreement shall be construed as a transfer of copyright ownership to the Model.

\subsection{Right of Use by Photographer/Company}
The Photographer and/or Company shall have the unrestricted right to use, reproduce, distribute, publish, display, license, sell, or otherwise exploit the Materials in any format or media now known or later developed, subject only to the terms outlined in this Agreement.

\subsection{No Ownership or License to Model}
The Model does not acquire any ownership interest in the Materials. Unless otherwise agreed in writing, the Model may not sell, license, edit, alter, or commercially exploit the Materials.

\subsection{Permitted Personal Use}
If applicable, the Model may use the Materials for personal, non-commercial purposes (such as portfolios or social media), provided that:

\begin{itemize}
  \item Proper credit is given to the Photographer where reasonably possible.
  \item The Materials are not altered beyond basic cropping or resizing without written consent.
  \item The use does not imply endorsement of any product or service without authorization.
\end{itemize}

\subsection{Third-Party Licensing}
The Photographer and/or Company may license the Materials to third parties without further consent from or compensation to the Model, unless otherwise specified in a separate written agreement.

\subsection{Archiving and Retention}
The Photographer and/or Company is not obligated to retain the Materials for any specific period unless otherwise agreed in writing.

%%% End of document (ownership.tex)